Data Processing

### 2020-01-24 analysis/data_processing.Rmd
update visualizations

ggplot() +
  geom_hline(yintercept = .5, lty=2, size = 1)+
  geom_line(data = samples, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
  geom_line(data = maps, aes(x = age, y = y), size = 1)+
  geom_jitter(data = p_data,aes(x = age, y= correct), width = .00, height = .01, alpha = .2)+
  geom_pointrange(data = p_data2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .5, position = position_dodge(width = .2), pch = 5, col = "#6866cc")+
  labs(x="Age",y="Proportion correct")+
  facet_wrap(~task, nrow = 2)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F, col = F)+
  coord_fixed(ratio = 2)
```

>>>>

ggplot() +
  geom_hline(yintercept = .5, lty=2, size = 1)+
  geom_line(data = samples, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
  geom_line(data = maps, aes(x = age, y = y), size = 1)+
  geom_jitter(data = p_data,aes(x = age, y= correct), width = .00, height = .01, alpha = .2)+
  geom_pointrange(data = p_data2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .5, position = position_dodge(width = .2), pch = 5, col = "#6866cc")+
  labs(x="Age",y="Proportion correct")+
  facet_wrap(~task, nrow = 2)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F, col = F)+
  coord_fixed(ratio = 2)+
  ggsave("../graphs/task_results.png")
```
